Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-12-06 manuscript/supplemental_material.Rnw
add short captions for supplemental figures

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CRH" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.37))
@ 
\caption{\genetreeexplanation{\textit{CRH}}}
\label{fig:crh_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="KISS1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.7))
@ 
\caption{\genetreeexplanation[0.1]{\textit{KISS1}}}
\label{fig:kiss1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PAPPA"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSSSCG00000005498","ENSG00000182752"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.15))
@ 
\caption{\genetreeexplanation[0.1]{\textit{PAPPA}}}
\label{fig:pappa_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="ADAM12" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c("ENSMODG00000010538","ENSSSCG00000010746"),
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.25))
@ 
\caption{\genetreeexplanation{\textit{ADAM12}}}
\label{fig:adam12_evolution_tree}
\end{figure}

@@

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption=c("\\lineagetableexplanationtypeiii{\\human}{all other species}","\\human lineage specific genes")
                                    label="tab:human_lineage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

@@

print(ggplot(cptlh[FPKM > 0.9,],aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("Gene Expression (FPKM)")+
      theme_bw() +
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic",size=5),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption{Housekeeping genes excluded from the Core Placenta Transcriptome.
  \Sexpr{cptlh[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed ($\mathrm{FPKM} \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied which are housekeeping genes~%
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited}
  ordered (from top to bottom) by median expression.}
\label{fig:core_placenta_transcriptome_housekeeping}
\end{figure}

@@

\caption{Distribution shape of housekeeping genes in placentas out of

>>>>

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CRH" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.37))
@ 
\caption[Gene tree of \textit{CRH} Expression]{\genetreeexplanation{\textit{CRH}}}
\label{fig:crh_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="KISS1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.7))
@ 
\caption[Gene tree of \textit{KISS1} Expression]{\genetreeexplanation[0.1]{\textit{KISS1}}}
\label{fig:kiss1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PAPPA"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSSSCG00000005498","ENSG00000182752"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.15))
@ 
\caption[Gene tree of \textit{PAPPA} Expression]{\genetreeexplanation[0.1]{\textit{PAPPA}}}
\label{fig:pappa_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="ADAM12" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c("ENSMODG00000010538","ENSSSCG00000010746"),
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.25))
@ 
\caption[Gene tree of \textit{ADAM12} Expression]{\genetreeexplanation{\textit{ADAM12}}}
\label{fig:adam12_evolution_tree}
\end{figure}

@@

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption=c("\\lineagetableexplanationtypeiii{\\human}{all other species}","\\human lineage specific genes"),
                                    label="tab:human_lineage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

@@

print(ggplot(cptlh[FPKM > 0.9,],aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("Gene Expression (FPKM)")+
      theme_bw() +
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic",size=5),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption[Housekeeping genes excluded from the Core Placenta Transcriptome]{
  Housekeeping genes excluded from the Core Placenta Transcriptome.
  \Sexpr{cptlh[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed ($\mathrm{FPKM} \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied which are housekeeping genes~%
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited}
  ordered (from top to bottom) by median expression.}
\label{fig:core_placenta_transcriptome_housekeeping}
\end{figure}

@@

\caption[Distribution shape of housekeeping genes in placentas]{
  Distribution shape of housekeeping genes in placentas out of
